Motion planning for assessing accessibility of protein tunnels

### 2017-09-09 paper.tex
missing $$ for times

In the following experiments, we measure performance of the methods using the traversability rate, which is the percentage of the protein dynamic frames that are traversable.
A frame is considered traversable, if at least one trajectory out of 20 (the number of initial configurations $|\QI|$) \times 10 trials approaches the active site to the distance less than 2~\AA.

@@

\begin{table}
\centering
\caption{\label{tab::main}
    Traversability of the tunnels for ligands with 50 conformations. 
    The number after $/$ denotes the number of atoms.
}
\small
\renewcommand{\tabcolsep}{3pt}
{\small
\input graph.tex
}
\end{table}

>>>>

In the following experiments, we measure performance of the methods using the traversability rate, which is the percentage of the protein dynamic frames that are traversable.
A frame is considered traversable, if at least one trajectory out of 20 (the number of initial configurations $|\QI|$) $\times$ 10 trials approaches the active site to the distance less than 2~\AA.

@@

\begin{table}
\centering
\caption{\label{tab::main}
    Traversability of the tunnels for ligands with 50 conformations. 
    The number after '$/$' denotes the number of atoms.
}
\small
\renewcommand{\tabcolsep}{3pt}
{\small
\input graph.tex
}
\end{table}
